Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
Comments

\begin{lemma}	\label{lemma:rebalancecost}
    The cost of repartitioning at Line \ref{line:rebalance} is at most $2\cdot\OPT$.
\end{lemma}
\begin{proof}
    Consider the repartitioning that transforms $P_{t-1}$ to $P_t$ upon the request $\sigma_t$.
    Let $M \subset V$ denote the set of nodes that migrate during this process.
	Let $M^-$ and $M^+$ denote the subset of nodes that (respectively)
    enter or leave their original cluster during the repartitioning.    
    Then,
    $M = M^+ \cup M^-$.
    Since \maciek{at least?} $|M^-|$ nodes are not in their original cluster before the repartitioning (i.e., in $P_{t-1}$),
    the distance before the repartitioning is $\dist(P_{t-1},P_I) \geq | M^-|$.
    Analogously,
     the distance afterwards is \maciek{at least?} $\dist(P_{t},P_I) \geq | M^+|$.
    Thus,
    $|M| \leq \dist(P_{t-1},P_I) + \dist(P_{t},P_I)$.
    By Property \ref{prop:dist<OPT},
    $\dist(P_{t-1},P_I) , \dist(P_{t},P_I) \leq \Delta \leq \OPT$
    and thereby we have	
    $|M| \leq 2\cdot\OPT$.
    \maciek{the comma between $\dist$ is confusing. BOTH are bounded? If so, expand the sentence and write both individual bounds.}
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	\mahmoud{still proof sketch}
	Let $C^{t}_{\set{u,v}}$ denote the  value of $C_{\set{u,v}}$ immediately after arrival of $\sigma_t$.
	Assume on request $\sigma_{t}=\set{u,v}$,
	Alg collocates the pair,
	which means $ C^t_{\set{u,v}} = \lambda$ immediately before Alg resets the counter.
	Let $\sigma_{t''}, t''<t$ be the last request (before $\sigma_{t}$)
	on which Alg collocates $\set{u,v}$.
	Let $t'$ s.t.~$t'' < t' < t$ be the  time when Alg separates $\set{u,v}$
	in order to collocate some other pair that shares a node with $\set{u,v}$,
	denoted by $\set{u,v'}, v' \neq v$.
	%e.g., the request $\sigma_{t'} = \set{u,v'}$.
	%By Alg's definition,
	%$C^{t'}_{\set{u,v'}}  = C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to $\set{u,v}$
	between times $t'$ and $t$ by $\sigma_{\set{u,v}}[t',t]$.
	Thus,
	$| \sigma_{\set{u,v}}[t',t] | = \lambda$.
	The overall cost of requests that increase the counter,
	i.e.~requests in $\sigma_{\set{u,v}}[t',t]$,
	and the moving cost,
	incurred by Alg is $\lambda + 2\alpha$.
	%That is, the cost of all requests in $\sigma_{\set{u,v}}[t',t]$.
	We distinguish three cases for the cost incurred by OPT due to $\set{u,v}$.
	Case i)
	OPT has $\set{u,v}$ separated (in OPT's configuration) during $[t',t]$
	and therefore it pays $\lambda$.
	We charge OPT $\lambda/2 = \alpha$.
	The remaining cost will be used in a latter case.
	Case ii)  
	OPT collocates $\set{u,v}$ some time during $[t'',t]$.
	Any cost that we charge to OPT upon $\sigma_{t''}$,
	accounts for OPT's actions before $t''$.
	Therefore in this case,
	we charge OPT the (unaccounted) cost $\alpha$.
	Case iii)
	OPT has $\set{u,v}$ collocated before $t''$ and keeps them collocated during $[t'',t]$.
	Obviously in this case OPT doesn't pays any cost for requests in $\sigma_{\set{u,v}}[t'',t]$ and
	we can't charge it directly.
	However,
	OPT must pay $\lambda$ for all requests in $\sigma_{\set{u,v'}}[t'',t']$,
	and we charge it partially to OPT at $t'$ (as in Case i).
	Since we always charge OPT no more than $\alpha$,
	we can charge OPT another $\alpha$,
	the remaining cost of requests $\sigma_{\set{u,v'}}[t'',t']$.
	Intuitively,
	at $t$,
	we charge OPT $\alpha$ for separating $\set{u,v}$ at $t'$.
	It can be easily verified that any deviation from these cases only increases the cost to OPT.
	Thus,
	OPT pays at least $\alpha$ for each collocation performed by Alg,
	which gives the competitive ratio 
	$(\lambda + 2\alpha)/ \alpha = 4$.

@@

>>>>

\begin{lemma}	\label{lemma:rebalancecost}
    The cost of repartitioning at Line \ref{line:rebalance} is at most $2\cdot\OPT$.
\end{lemma}
\begin{proof}
    Consider the repartitioning that transforms $P_{t-1}$ to $P_t$ upon the request $\sigma_t$.
    Let $M \subset V$ denote the set of nodes that migrate during this process.
	Let $M^-$ and $M^+$ denote the subset of nodes that (respectively)
    enter or leave their original cluster during the repartitioning.    
    Then,
    $M = M^+ \cup M^-$.
    Since \maciek{at least?} $|M^-|$ nodes are not in their original cluster before the repartitioning (i.e., in $P_{t-1}$),
    the distance before the repartitioning is $\dist(P_{t-1},P_I) \geq | M^-|$.
    Analogously,
     the distance afterwards is $\dist(P_{t},P_I) \geq | M^+|$.
    Thus,
    $|M| \leq \dist(P_{t-1},P_I) + \dist(P_{t},P_I)$.
    By Property \ref{prop:dist<OPT},
    $\dist(P_{t-1},P_I) , \dist(P_{t},P_I) \leq \Delta \leq \OPT$
    and thereby we have	
    $|M| \leq 2\cdot\OPT$.
    \maciek{the comma between $\dist$ is confusing. BOTH are bounded? If so, expand the sentence and write both individual bounds.}
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	\mahmoud{still proof sketch}
	Let $C^{t}_{\set{u,v}}$ denote the  value of $C_{\set{u,v}}$ immediately after arrival of $\sigma_t$.
	Assume on request $\sigma_{t}=\set{u,v}$,
	Alg collocates the pair,
	which means $ C^t_{\set{u,v}} = \lambda$ immediately before Alg resets the counter.
	Let $\sigma_{t''}, t''<t$ be the last request (before $\sigma_{t}$)
	on which Alg collocates $\set{u,v}$.
	Let $t'$ s.t.~$t'' < t' < t$ be the  time when Alg separates $\set{u,v}$
	in order to collocate some other pair that shares a node with $\set{u,v}$,
	denoted by $\set{u,v'}, v' \neq v$.
	%e.g., the request $\sigma_{t'} = \set{u,v'}$.
	%By Alg's definition,
	%$C^{t'}_{\set{u,v'}}  = C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to $\set{u,v}$
	between times $t'$ and $t$ by $\sigma_{\set{u,v}}[t',t]$.
	Thus,
	$| \sigma_{\set{u,v}}[t',t] | = \lambda$.
	The overall cost of requests that increase the counter,
	i.e.~requests in $\sigma_{\set{u,v}}[t',t]$,
	and the moving cost,
	incurred by Alg is $\lambda + 2\alpha$.
  %That is, the cost of all requests in $\sigma_{\set{u,v}}[t',t]$.

	We distinguish three cases for the cost incurred by OPT due to $\set{u,v}$.

  \begin{enumerate}
  \item Case i)
	OPT has $\set{u,v}$ separated (in OPT's configuration) during $[t',t]$
	and therefore it pays $\lambda$.
	We charge OPT $\lambda/2 = \alpha$.
	The remaining cost will be used in a latter case.

  \item Case ii)  
	OPT collocates $\set{u,v}$ some time during $[t'',t]$.
	Any cost that we charge to OPT upon $\sigma_{t''}$,
	accounts for OPT's actions before $t''$.
	Therefore in this case,
	we charge OPT the (unaccounted) cost $\alpha$.

  \item Case iii)
	OPT has $\set{u,v}$ collocated before $t''$ and keeps them collocated during $[t'',t]$.
	Obviously in this case OPT doesn't pays any cost for requests in $\sigma_{\set{u,v}}[t'',t]$ and
	we can't charge it directly.
	However,
	OPT must pay $\lambda$ for all requests in $\sigma_{\set{u,v'}}[t'',t']$,
	and we charge it partially to OPT at $t'$ (as in Case i).
	Since we always charge OPT no more than $\alpha$,
	we can charge OPT another $\alpha$,
	the remaining cost of requests $\sigma_{\set{u,v'}}[t'',t']$.
	Intuitively,
	at $t$,
  we charge OPT $\alpha$ for separating $\set{u,v}$ at $t'$.
  \end{enumerate}

	It can be easily verified that any deviation from these cases only increases the cost to OPT.
	Thus,
	OPT pays at least $\alpha$ for each collocation performed by Alg,
	which gives the competitive ratio 
	$(\lambda + 2\alpha)/ \alpha = 4$.

@@

\maciek{Missing the case of the first-time collocation. What if t' does not exist? What if t'' does not exist?}
\maciek{Define $C^t$ to use once}
\maciek{"It can be easily verified"... True, but avoid such formulation. Something along these lines: if opt migrates earlier than t', then additionally pays for X, if later than Y.}
\maciek{"Thus, OPT pays ... which gives the competitive ratio" It is too early to give the competitive ratio if in the next paragraph we consider yet another case}
